\textbf{ Spectrophotometric parallaxes with linear models:\\ Accurate distances for luminous red-giant stars }

### 2019-06-03 paper/sp.tex
caption update

We optimize two models, one for Training Set A and one for Training Set B.
The two models are applied to the two splits of the Parent Sample, Parent Sample
A and Parent Sample B, using the A-trained model on Parent Sample B and
\foreign{vice versa}.
For the purposes of assessing the accuracy and precision of the model, this
train-and-test framework constitutes a two-fold cross-validation.
Results of this cross-validation are shown in \figurename~\ref{fig:xval}.
For the stars with highest \gaia-measured parallax signal-to-noise,
the spectrophotometric model is predicting the \gaia\ parallaxes with little bias
and a scatter of less than 9~percent.
\begin{figure}
\includegraphics[width=\textwidth]{residuals.pdf}
\caption{The predictive accuracy of the model, in the two-fold cross-validation.
  Each panel shows \gaia\ astrometric parallaxes $\gparallax_n$ on the horizontal axis
  and our spectrophotometric parallaxes $\sparallax$ on the vertical axis.
  The left panel shows the full Training Set (both A and B combined),
  and the right panel shows a
  subset of stars with very high astrometric parallax signal-to-noise. This latter
  set plays no particular role in the method, but it can be used to demonstrate or
  assess the prediction precision. The fractional precision of the prediction in the
  right panel is better than 9 percent. Note that by construction, there can be no negative
  spectrophotometric parallaxes; that is, the quantity plotted on the vertical axis is
  positive-definite.\label{fig:xval}}
\end{figure}

@@

It is also interesting to compare these estimates to other, previous
spectroscopic distance efforts.
We performed comparisons with two other efforts (\citealt{sch, que}).
In both cases, the agreement is better at smaller distances (larger
parallaxes) and worse at larger distances, with the distances
(parallaxes) presented here being smaller (larger) on average than the other
investigation results for the very most distant (and hence most difficult) stars.
In detail, the comparison with the larger sample (\citealt{sch})
are better:
The scatter is at the 15-percent level for stars at distances
$<8$\,kpc), and there is no visible bias between the results at these
distances.
The distances presented here also compare well with those from a recent
machine-learning approach (\citealt{leung}), which appeared while this
paper was under review.

>>>>

We optimize two models, one for Training Set A and one for Training Set B.
The two models are applied to the two splits of the Parent Sample, Parent Sample
A and Parent Sample B, using the A-trained model on Parent Sample B and
\foreign{vice versa}.
For the purposes of assessing the accuracy and precision of the model, this
train-and-test framework constitutes a two-fold cross-validation.
Results of this cross-validation are shown in \figurename~\ref{fig:xval}.
For the stars with highest \gaia-measured parallax signal-to-noise,
the spectrophotometric model is predicting the \gaia\ parallaxes with little bias
and a scatter of less than 9~percent.
\begin{figure}
\includegraphics[width=\textwidth]{residuals_inclduing_parent_sample.pdf}
\caption{The predictive accuracy of the model, in the two-fold cross-validation.
  Each panel shows \gaia\ astrometric parallaxes $\gparallax_n$ on the horizontal axis
  and our spectrophotometric parallaxes $\sparallax$ on the vertical axis.
  The points are colored by spectroscopic (\apogee) signal-to-noise ratio.
  The left panel shows the full Parent Sample,
  the middle panel shows the Training Set (both A and B combined),
  and the right panel shows a
  subset of stars with very high astrometric parallax signal-to-noise. This latter
  set plays no particular role in the method, but it can be used to demonstrate or
  assess the prediction precision. The fractional precision of the prediction in the
  right panel is better than 9 percent. Note that by construction, there can be no negative
  spectrophotometric parallaxes; that is, the quantity plotted on the vertical axis is
  positive-definite.\label{fig:xval}}
\end{figure}

@@

It is also interesting to compare these estimates to other, previous
spectroscopic distance efforts.
We performed comparisons with two other efforts (\citealt{sch, que}).
In both cases, the agreement is better at smaller distances (larger
parallaxes) and worse at larger distances, with the distances
(parallaxes) presented here being smaller (larger) on average than the other
investigation results for the very most distant (and hence most difficult) stars.
In detail, the comparison with the more recent sample (\citealt{que})
are better:
The scatter is at the 15-percent level for stars at distances
$<8$\,kpc), and there is no visible bias between the results at these
distances.
The distances presented here also compare well with those from a recent
machine-learning approach (\citealt{leung}), which appeared while this
paper was under review.
